---
title: "Weight of Fish"
author: "Taylor Stohl"
date: "Summer 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
read.csv 
Fishdata <- read.csv(file = "Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

#Build the best regression model you can that predicts the weight of perch, Bream, and Smelt.
#Using only two predictor variables


# Methods

First the data needed to be read opened from the csv file. The appropriate r command was used to achive this and was title Fishdata. Fishdata includes 6 variables total. These variables are Weight, Lenghth1, Lenghth2, Lenghth3, Height, and Weight. This project is trying to find out what two variables best describe weight in 3 species of fish. Perch, Bream, and Smelt are the three species.
Fishdata also includes the character variable species and that needs to be removed to effectively read the data. Appropriate R commands are used to extract the numerical variables from the character variable "species" for each  of the three types of fish. 

# Perch

```{r}
perch <- filter(Fishdata,Species == "Perch")
perch <- select(perch,-1)
``` 

This R command breaks perch apart from Fishdata and creates another subset. There are 56 observations of perch and 6 variables. These are the same previous variables.

## Model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


This model includes 5 regression models that have varying variables in each and explain the perch fish weight. The numbers of variables in each model range from 1 to 5 and the most effective model will be seen at the top, while the lowest will be seen at the bottom. 

The two best elemental regression models to explain what the fish's weight is appears to be Height and Width. This model is also the best possible model as it can be seen at the highest location on this plot. The adjusted R-squared is around 0.94.

The best model with two regressors is model 2, as is illustated in this plot. 

## Summaries

```{r}
which.max(summary.out$adjr2)
```


The best model of all of them is model 2. The best model that has two regressors is also model 2.


```{r}
summary.out$which[2,]
```

This summary clarifies what regressors to use to make the most effective model that displays fish weight. These two variables that have TRUE next to them are the ones that are included and they are Heighth and Width; just as illustated in the model. 

# Bream


```{r}
Bream <- filter(Fishdata,Species == "Bream")
Bream <- select(Bream,-1)
``` 

This R command breaks Bream apart from Fishdata and creates another subset. There are 35 observations of Bream and 6 variables. These are the same previous variables.

## Model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

For the model dedicated to the Bream species of fish, The best two regressors to use are Length 2 and Height. This model differentiates from the model for the perch species because the best model possible in this model is actually Lenghth1, Heighth, and Width. This problem wants to what what model with two regressors is the best and that is model 2 that has Lenghth 2 and Height. Approximating with what can be seen in this model The adjusted R- squared for model 2 looks to be about 0.93.


## Summaries


```{r}
which.max(summary.out$adjr2)
```

The best model is model 3. However, the best model that only includes two regressors to explain the fish's wight is model 2. These variable are Length 2 and Height. 


```{r}
summary.out$which[2,]
```

This summary clarifies which variables are included in the best model for onlt 2 regressors. These variables are clearly Lenghth 2 and Heighth. 

# Smelt

```{r}
Smelt <- filter(Fishdata,Species == "Smelt")
Smelt <- select(Smelt,-1)
``` 

This R command breaks Smelt apart from Fishdata and creates another subset. There are only 14 observations of Bream and 6 variables. These are the same previous variables.

## Model 

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This model is dedicated to the data for the species of fish called Smelt. The best two element regression model to describe weight is Lenghth 2 and Width. The best model possible for Smelt, however, is a 4 variable model and includes Lenghth1, Length2, Height, and Width. The adjusted R-squared for the two variable model looks to be about 0.96 and some change. 

## Summaries


```{r}
which.max(summary.out$adjr2)
```

The best model possible for explaining smelt weight is model 4. The best model with only two regressors, however, is model 2.


```{r}
summary.out$which[2,]
```

This is a summary that clarifies what two variables make up the best model with only 2 regressors. As seen, Length2 and Width are the best pick.

